---
title: "Untitled"
author: "Zhongyuan"
date: "2019/11/14"
output: html_document
---

## R Markdown
Possible research question:
1.How did teachers and parents evaluate kids differently or similarly from these three aspects of Persistency, Ability to concentrate and Learning Desire? (in degree, can we quantify the difference/similarity?)
(Periods of time selected were Fall Kindergarten, Spring Kindergarten and Spring First Grade)

matched items are:
P10--T23
P15--T24
P22--T14

2. How did the students improve in these aspects of Getting things well-organized,Learning Desire, Independence on Work, Adapability to changes, Persistence and Ability to concentrate in teachers' eye? (From T1~G6)

3.Predict?the 


```{r}
library(haven)
df<-read_spss("2010070_atl_spss.sav")
df<-na.omit(df)

#Keep data only from period FALL KINTERGARTEN; SPRING KINTERGARTEN; SPRING FIRST GRADE

library(dplyr)
df2<-df%>%
  dplyr::select(CHILDID,contains("P"),contains("T1"),contains("T2"),contains("T4"))

df_LEARN<-df%>%
  dplyr::select(P1LEARN,P2LEARN,P4LEARN,T1LEARN,T2LEARN,T4LEARN)

COR_LEARN<-cor(df_LEARN)

library(corrplot)
corrplot(COR_LEARN, order="AOE", method="circle", tl.pos="ld", type="lower",        
tl.col="blue", tl.cex=0.8, tl.srt=20, 
        addCoef.col="black", addCoefasPercent = TRUE,
        sig.level=0.50, insig = "blank")


```

According to the correlation figure, Approaches to learning scale: 
P1LEARN V.S T1LEARN; P2LEARN V.S T2LEARN; P3LEARN V.S T3LEARN are moderately correlated
P1LEARN V.S P2LEARN 54; P1LEARN V.S P4LEARN 24; P2LEARN V.S P4LEARN
T1LEARN V.S T2LEARN 54; T1LEARN V.S T4LEARN 24; T2LEARN V.S T4LEARN 

moderate to week correlation 

```{r}
#descriptive statistic
library(psych)
describe(df_LEARN)

```

```{r}
#t-test to see the difference
t.test(df_LEARN$P1LEARN,df_LEARN$T1LEARN) #statistically significant
t.test(df_LEARN$P2LEARN,df_LEARN$T2LEARN) #statistically significant
t.test(df_LEARN$P4LEARN,df_LEARN$T4LEARN) #no statistically significant

```


```{r cars}
df_srs<-df[,1:9]
df_srs_items<-df[,-(2:9)]
summary(df_srs)


summary(cars)